\cvevent{\textbf{Backend for Mobile Application (EvenTeam LLC — Startup)}}{08/2021 - 02/2022}
\begin{itemize}
\item Analyzed project requirements, coordinated with customer contacts, and developed microservices (9 modules) for the backend.
\item Created unit tests, optimized existing code, and ensured maintainability, scalability, and performance.
\item Facilitated communication between engineers and the design agency, focusing on a homogeneous architecture using Java Spring Boot and other cloud technologies.
\end{itemize}

\divider

\cvevent{\textbf{Development of Travel App Backend}}{03/2022 - 11/2022}
\begin{itemize}
\item Developed microservices to enhance the flexibility of the web application.
\item Automated build and deploy processes and integrated Chef Server API for system management.
\item Implemented monitoring functionalities and resolved bugs to maintain software quality.
\end{itemize}

\divider

\cvevent{\textbf{LinguaMat Development (Startup)}}{03/2021 - 02/2022}
\begin{itemize}
\item Conducted requirement gathering and business analysis, coordinating with customer contacts.
\item Developed microservices, set up servers, optimized code, and created unit tests.
\item Utilized Java Spring Boot, Docker, Kubernetes, CI/CD tools for search engine, messenger, and order functionalities.
\end{itemize}

\cvsection{\faStar \; Languages}

\cvskill{English - C2}{5}
\divider

\cvskill{German - B2}{4}
\divider

\cvskill{Russian - C1}{5}
\divider

\cvskill{Turkish - C2}{5}
\divider

\cvskill{Azerbaijani - Native Speaker}{5}
